A Decision Procedure for (Co)datatypes in SMT Solvers

### 2015-11-09 jour/jour.tex
Minor

\begin{figure}[t!]
\normalsize
\centering
\begin{enumerate}
\item Let $\mathcal{U}$ be a partition of the codatatype equivalence classes of $\Ec$ such that $\ec{t} =_{\mathcal{U}} \ec{u}$ for distinct $\ec{t}, \ec{u}$ if and only if:
\begin{itemize}
\item $\const{C}( t_1, \ldots, t_k ) \in \ec{t}$ and $\const{C}( u_1, \ldots, u_k ) \in \ec{u}$.
\end{itemize}
\item Repeat until $\mathcal{U}$ is unchanged
\begin{enumerate}
\item $\mathcal{U}' := \emptyset$
\item for each $U_i \in \mathcal{U}$:
\begin{itemize}
\item[\ ] Let $\mathcal{U}_i$ be a partition of $U_i$ such that $\ec{t} =_{\mathcal{U}_i} \ec{u}$ for distinct $\ec{t}, \ec{u}$ if and only if:
\begin{itemize}
\item $\const{C}( t_1, \ldots, t_k ) \in \ec{t}$ and $\const{C}( u_1, \ldots, u_k ) \in \ec{u}$, and
\item $\ec{t_j} =_{\mathcal{U}} \ec{u_j}$ for each $j = 1, \ldots, k$.
\end{itemize}
\item[\ ] $\mathcal{U}' := \mathcal{U}' \cup \mathcal{U}_i$.
\end{itemize}
\item $\mathcal{U} := \mathcal{U}'$
\end{enumerate}
\item If distinct $\ec{t}, \ec{u} \in U$ for some $U \in \mathcal{U}$, apply \rn{Unique} to $t,u$.
\end{enumerate}
\vspace*{-2pt} %% TYPESETTING HACK
\caption{\,Algorithm for checking Uniqueness.
}
\label{fig:uniqueness-algo}
\end{figure}

@@

\flushleft $\mathrm{traverse}( \ec{t}, U, P )$:
\begin{enumerate}
\item If $\ec{t} \in P$, apply \rn{Acyclic} to $t$.
\item If $\ec{t} \in U$
\begin{enumerate}
\item If $\const{C}( t_1, \ldots, t_k ) \in \ec{t}$, then for each $j = 1, \ldots k$,
\begin{itemize}
\item[\ ] $\mathrm{traverse}( \ec{t_j}, U, P \cup \{ \ec{t} \} )$
\end{itemize}
\item $U := U \textbackslash \{ \ec{t} \}$.
\end{enumerate}
\end{enumerate}
\vspace*{-2pt} %% TYPESETTING HACK
\caption{\,Algorithm for checking Acyclic.
}
\label{fig:acyclic-algo}
\end{figure}

>>>>

\begin{figure}[t!]
\normalsize
\centering
\begin{enumerate}
\item Let $\mathcal{U}$ be a partition of the equivalence classes of $\Ec$ such that $\ec{t} =_{\mathcal{U}} \ec{u}$ for distinct $\ec{t}, \ec{u}$ if and only if:
\begin{itemize}
\item $t\typ{\delta}$, $u\typ{\delta}$ where $\delta \in \Codata$, and $\const{C}( t_1, \ldots, t_k ) \in \ec{t}$ and $\const{C}( u_1, \ldots, u_k ) \in \ec{u}$.
\end{itemize}
\item Repeat until $\mathcal{U}$ is unchanged
\begin{enumerate}
\item $\mathcal{U}' := \emptyset$
\item for each $U_i \in \mathcal{U}$:
\begin{itemize}
\item[\ ] Let $\mathcal{U}_i$ be a partition of $U_i$ such that $\ec{t} =_{\mathcal{U}_i} \ec{u}$ for distinct $\ec{t}, \ec{u}$ if and only if:
\begin{itemize}
\item $\const{C}( t_1, \ldots, t_k ) \in \ec{t}$ and $\const{C}( u_1, \ldots, u_k ) \in \ec{u}$, and
\item $\ec{t_j} =_{\mathcal{U}} \ec{u_j}$ for each $j = 1, \ldots, k$.
\end{itemize}
\item[\ ] $\mathcal{U}' := \mathcal{U}' \cup \mathcal{U}_i$.
\end{itemize}
\item $\mathcal{U} := \mathcal{U}'$
\end{enumerate}
\item If distinct $\ec{t}, \ec{u} \in U$ for some $U \in \mathcal{U}$, apply \rn{Unique} to $t,u$.
\end{enumerate}
\vspace*{-2pt} %% TYPESETTING HACK
\caption{\,Algorithm for checking Uniqueness.
}
\label{fig:uniqueness-algo}
\end{figure}

@@

\flushleft $\mathrm{traverse}( \ec{t}, U, P )$:
\begin{enumerate}
\item If $\ec{t} \in P$, apply \rn{Acyclic} to $t$.
\item If $\ec{t} \in U$,
\begin{enumerate}
\item If $\const{C}( t_1, \ldots, t_k ) \in \ec{t}$, then for each $j = 1, \ldots k$,
\begin{itemize}
\item[\ ] $\mathrm{traverse}( \ec{t_j}, U, P \cup \{ \ec{t} \} )$
\end{itemize}
\item $U := U \textbackslash \{ \ec{t} \}$.
\end{enumerate}
\end{enumerate}
\vspace*{-2pt} %% TYPESETTING HACK
\caption{\,Algorithm for checking Acyclic.
}
\label{fig:acyclic-algo}
\end{figure}
